A comparative analysis of penalized linear mixed models in structured genetic data

### 2020-12-11 supplement.tex
Supplement

\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth, height=\textheight, keepaspectratio]{figures/niter_perLambda_point.png}
    \caption{The number of iterations per $\lambda$ value for LMM-Lasso-Rakitsch and LMM-Lasso-ggmix across varying sample sizes with Independent Subpopulations data, coarse subpopulation structure, $\eta = 0.8$, and $\xi = 0.8$, and dichotomous-discordant environmental effect structure. Note that 100 is the maximum number of iterations for both implementations of LMM-Lasso, so that numerous incidences of 100 iterations may indicate lack of model convergence.}
    \label{fig:niter}
\end{sidewaysfigure}

>>>>

\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth, height=\textheight, keepaspectratio]{figures/niter_perLambda_point.png}
    \caption{The number of iterations per $\lambda$ value for LMM-lasso-Rakitsch and LMM-lasso-ggmix across varying sample sizes with Independent Subpopulations data, coarse subpopulation structure, $\eta = 0.8$, and $\xi = 0.8$, and dichotomous-discordant environmental effect structure. Note that 100 is the maximum number of iterations for both implementations of LMM-lasso, so that numerous incidences of 100 iterations may indicate lack of model convergence.}
    \label{fig:niter}
\end{sidewaysfigure}
